Comparative study of requantization of time-dependent mean-field for pairing dynamics

### 2017-10-11 draft1.1.tex
updated figures, added appendix

\begin{figure}[htbp]
 \begin{center}
%  \includegraphics[width=60mm,angle=-90]{images/phase.eps}
 \end{center}
 \caption{Energy contour plot for $\Omega_1=\Omega_2=8$ and $N=16$.
	The lines indicate the TDHFB trajectories fulfilling
	the EBK quantization condition of Eq. (\ref{EBK}).
	}
 \label{fig:phase_space}
\end{figure}

@@

We apply semiclassical approach to the two-level pairing model.
The invariant measure in SU(2)$\otimes$SU(2) is 
\begin{align}
%	d\mu(Z) &= \prod_{l=1,2} \frac{S_l+1}{\pi}(1+|Z_l|^2)^{-2}d{\rm Re}Z_ld{\rm Im}Z_l \\
%  &= \prod_l \frac{S_l+1}{4\pi}\sin{\theta_l}d\theta_ld\phi_l \\
%  &= \frac{S_1+1}{4\pi}\frac{S_2+1}{4\pi}\frac{1}{S_1S_2}d\Phi d\Pi d\phi d\pi .
d\mu(Z) &= \prod_l \frac{\Omega_l+2}{2\pi}(1+|Z_l|^2)^{-2}d{\rm Re}Z_ld{\rm Im}Z_l \\
  &= \prod_l \frac{\Omega_l+2}{8\pi}\sin{\theta_l}d\theta_ld\phi_l \\
	&= \left(\prod_{l=1,2} \frac{1+2\Omega_l^{-1}}{4\pi}\right)
             d\Phi dJ d\phi dj .
\end{align}
In the last equation, we transform the canonical coordinates
by Eqs. (\ref{phi}) and (\ref{pi}).
%In two-level system, we can transform the canonical coordinates by (\ref{phi}) and (\ref{pi}).
%After coordinate transformation, the Hamilton's equations are
%\begin{align}
%\left\{
%\begin{array}{c}
%  \dot{\Phi} = \frac{\partial\mathcal{H}}{\partial \Pi} \\
%  \dot{\Pi} = -\frac{\partial\mathcal{H}}{\partial \Phi} 
%\end{array}
%\right. \hspace{10mm} \left\{
%\begin{array}{c}
%  \dot{\phi} = \frac{\partial\mathcal{H}}{\partial \pi} \\
%  \dot{\pi} = -\frac{\partial\mathcal{H}}{\partial \phi} 
%\end{array}
%\right. , \label{Hamilton}
%\end{align}
%and the measure and action integral become
%\begin{align}
%  d\mu(Z) &= \frac{S_1+1}{4\pi}\frac{S_2+1}{4\pi}\frac{1}{S_1S_2}d\Phi d\Pi d\phi d\pi \\
%  \mathcal{T}(Z) &=  \int (\Pi d\Phi+\pi d\phi) = \Pi\Phi + \int \pi d\phi.
%\end{align}
%The above canonical variables contain an invariant number $\Pi$. Because two-level system has 2*2 dimensional phase space, we need to find another conservative number before applying (\ref{semi_wave_func}). This task can be accomplished by canonical transformation 
Since the particle number $J=N/2$ and the total energy $E$ are invariant,
the two-level pairing model is integrable.
Thus, we can construct the semiclassical wave function using
Eq. (\ref{semi_wave_func}).
%This task can be accomplished by canonical transformation 
%\begin{align}
%  (\phi, \pi)  \to (t, E)
%\end{align}
%where $E$ is total energy in classical system.
The action integral is given by
\begin{equation}
	\mathcal{T}_k(\Phi,\phi;J)
%	= \Pi\Phi + \int \pi(t) \frac{d\phi}{dt} dt .
	= J\Phi + \int^\phi_{-\pi} j' d\phi' 
	= \frac{N}{2}\Phi + \int^t_0   %_{\mathcal{H}(\phi,\pi)=E_k}
	j(t') \frac{d\phi}{dt'} dt' 
\equiv \mathcal{T}_{N,E_k}(\Phi,t) ,
\end{equation}
where the integration $\int j d\phi$ is performed on the $k$-th
closed trajectory of Eq. (\ref{EBK}), and
the variables $(\phi,j)$ are transformed into $(t,E)$.
%where $\pi(t)$ can be solved from the right side of (\ref{TDHFB_equation}). (i.e. 2D Runge-Kutta method) \par
The semiclassical wave function fulfilling the EBK quantization condition
becomes
\begin{align}
	\ket{\phi_k^N} &\propto \oint d\Phi \oint dt
	e^{i\mathcal{T}_{N,E_k}(\Phi, t)}
	\ket{\Phi,t}_{N,E_k} \nonumber \\
%  &\propto \sum_k \frac{1}{k!}\int_0^{2\pi}d\Phi e^{i(\Pi-k)\Phi}\sum_{j=0}^{k}C_j^{(E,k)}\ket{S_1,-S_1+j;S_2,-S_2+(k-j)} \label{semi_wave_func1}
  &\propto \sum_{m=0}^{J}C_m^{(E_k,J)}\ket{S_1,-S_1+m;S_2,-S_2+(J-m)} ,
	\label{semi_wave_func1}
\end{align}
with $S_l=\Omega_l/2$, $J=N/2$, and the coefficients
\begin{align}
  C_m^{(E_k,J)} &= {}_J C_m\int_0^T dt \exp{\left( i\int^t j(t') \dot{\phi}(t') dt'-i(J/2-m)\phi(t) \right)}A(q_1,S_1,m)A(q_2,S_2,J-m) ,\\
  & \hspace{5mm} A(q,S,m) = \left(\frac{1-q}{2}\right)^{m/2}\left(\frac{1+q}{2}\right)^{S-m/2}\sqrt{\frac{(2S)!m!}{(2S-m)!}}, \hspace{5mm} \nonumber
\end{align}
where $T$ is the period of the closed trajectory.
The TDHFB-requantized wave functions (\ref{semi_wave_func1}) are
eigenstates of the total particle number.
This is due to the integration over the global gauge angle $\Phi$,
which makes the particle number projection not only for the ground state
but also for excited states.
See Appendix for detailed derivation of Eq.~(\ref{semi_wave_func1}).

@@

\begin{figure}[htbp]
 \begin{center}
%  \includegraphics[width=60mm,angle=-90]{images/N50ex_energy.eps}
 \end{center}
 \caption{Excitation energies of $\ket{0_2^+}$, $\ket{0_3^+}$ and $\ket{0_4^+}$ in $N=50$ system.}
 \label{fig:N50energy}
\end{figure}

\begin{figure}[htbp]
 \begin{minipage}{1\hsize}
 \begin{center}
  \includegraphics[width=67mm,angle=-90]{images/N50Xeq0p5occ.eps}
 \end{center}
 \end{minipage}
 \begin{minipage}{1\hsize}
 \begin{center}
  \includegraphics[width=67mm,angle=-90]{images/N50Xeq2occ.eps}
 \end{center}
 \end{minipage}
 \caption{Occupation probability in excited $0^+$ states as a function of $\pi$ in $N=50$ system. The upper and lower panels display the results for $x=0.05$ and $x=0.2$, respectively. From the physical meaning of $\pi$, $-12.5$ corresponds to 0p50h configuration, $-11.5$ corresponds to 2p52h configuration, and so on.}
 \label{fig:N50_occ}
\end{figure}

\begin{figure}[htbp]
 \begin{minipage}{0.33\hsize}
 \begin{center}
%  \includegraphics[width=70mm,angle=-90]{images/N50Pad_exact.eps}
 \end{center}
 \captionsetup{labelformat=empty,labelsep=none}
 \end{minipage}
 \begin{minipage}{0.33\hsize}
 \begin{center}
%  \includegraphics[width=70mm,angle=-90]{images/N50Pad_Type1.eps}
 \end{center}
 \captionsetup{labelformat=empty,labelsep=none}
 \end{minipage}
 \begin{minipage}{0.33\hsize}
 \begin{center}
%  \includegraphics[width=70mm,angle=-90]{images/N50Pad_semiclassical.eps}
 \end{center}
 \captionsetup{labelformat=empty,labelsep=none}
 \end{minipage}
 \caption{The strength of pair additional transition from $N=48$ to $N=50$ system defined in (\ref{Pad}). The results of $\ket{0_1^+}\to\ket{0_1^+}$, $\ket{0_1^+}\to\ket{0_2^+}$, $\ket{0_2^+}\to\ket{0_1^+}$ and $\ket{0_2^+}\to\ket{0_2^+}$ are shown. Left panels: exact solution; Middle panels: canonical quantization; Right panels: semiclassical approach.}
 \label{fig:N50Pad}
\end{figure}

\begin{figure}[htbp]
 \begin{center}
%  \includegraphics[width=60mm,angle=-90]{images/N100ex_energy.eps}
 \end{center}
 \caption{Excitation energies of $\ket{0_2^+}$, $\ket{0_3^+}$ and $\ket{0_4^+}$ in $N=50$ system.}
 \label{fig:N50energy}
\end{figure}

\begin{figure}[htbp]
 \begin{minipage}{1\hsize}
 \begin{center}
  \includegraphics[width=67mm,angle=-90]{images/N100Xeq0p5occ.eps}
 \end{center}
 \end{minipage}
 \begin{minipage}{1\hsize}
 \begin{center}
  \includegraphics[width=67mm,angle=-90]{images/N100Xeq2occ.eps}
 \end{center}
 \end{minipage}
 \caption{Occupation probability in excited $0^+$ states as a function of $\pi$ in $N=50$ system. The upper and lower panels display the results for $x=0.05$ and $x=0.2$, respectively. From the physical meaning of $\pi$, $-12.5$ corresponds to 0p50h configuration, $-11.5$ corresponds to 2p52h configuration, and so on.}
 \label{fig:N50_occ}
\end{figure}

\begin{figure}[htbp]
 \begin{minipage}{0.33\hsize}
 \begin{center}
%  \includegraphics[width=70mm,angle=-90]{images/N100Pad_exact.eps}
 \end{center}
 \captionsetup{labelformat=empty,labelsep=none}
 \end{minipage}
 \begin{minipage}{0.33\hsize}
 \begin{center}
%  \includegraphics[width=70mm,angle=-90]{images/N100Pad_Type1.eps}
 \end{center}
 \captionsetup{labelformat=empty,labelsep=none}
 \end{minipage}
 \begin{minipage}{0.33\hsize}
 \begin{center}
%  \includegraphics[width=70mm,angle=-90]{images/N100Pad_semiclassical.eps}
 \end{center}
 \captionsetup{labelformat=empty,labelsep=none}
 \end{minipage}
 \caption{The strength of pair additional transition from $N=48$ to $N=50$ system defined in (\ref{Pad}). The results of $\ket{0_1^+}\to\ket{0_1^+}$, $\ket{0_1^+}\to\ket{0_2^+}$, $\ket{0_2^+}\to\ket{0_1^+}$ and $\ket{0_2^+}\to\ket{0_2^+}$ are shown. Left panels: exact solution; Middle panels: canonical quantization; Right panels: semiclassical approach.}
 \label{fig:N50Pad}
\end{figure}

@@

\begin{figure}[htbp]
 \begin{center}
%  \includegraphics[width=60mm,angle=-90]{images/N8ex_energy.eps}
 \end{center}
 \caption{Excitation energies of $\ket{0_2^+}$, $\ket{0_3^+}$ and $\ket{0_4^+}$ in $N=8$ system.}
 \label{fig:N8energy}
\end{figure}

\begin{figure}[htbp]
 \begin{minipage}{1\hsize}
 \begin{center}
  \includegraphics[width=67mm,angle=-90]{images/N8Xeq0p5occ.eps}
 \end{center}
 \end{minipage}
 \begin{minipage}{1\hsize}
 \begin{center}
  \includegraphics[width=67mm,angle=-90]{images/N8Xeq2occ.eps}
 \end{center}
 \end{minipage}
 \caption{Occupation probability in excited $0^+$ states as a function of $\pi$ in $N=8$ system. The upper and lower panels display the results for $x=0.05$ and $x=0.2$, respectively. From the physical meaning of $\pi$, $-2$ corresponds to 0p8h configuration, $-1$ corresponds to 2p10h configuration, and so on.}
 \label{fig:N8_occ}
\end{figure}

\begin{figure}[htbp]
 \begin{minipage}{0.33\hsize}
 \begin{center}
%  \includegraphics[width=70mm,angle=-90]{images/N8Pad_exact.eps}
 \end{center}
 \captionsetup{labelformat=empty,labelsep=none}
 \end{minipage}
 \begin{minipage}{0.33\hsize}
 \begin{center}
%  \includegraphics[width=70mm,angle=-90]{images/N8Pad_Type1.eps}
 \end{center}
 \captionsetup{labelformat=empty,labelsep=none}
 \end{minipage}
 \begin{minipage}{0.33\hsize}
 \begin{center}
%  \includegraphics[width=70mm,angle=-90]{images/N8Pad_semiclassical.eps}
 \end{center}
 \captionsetup{labelformat=empty,labelsep=none}
 \end{minipage}
 \caption{The strength of pair additional transition from $N=6$ to $N=8$ system defined in (\ref{Pad}). The results of $\ket{0_1^+}\to\ket{0_1^+}$, $\ket{0_1^+}\to\ket{0_2^+}$, $\ket{0_2^+}\to\ket{0_1^+}$ and $\ket{0_2^+}\to\ket{0_2^+}$ are shown. Left panels: exact solution; Middle panels: canonical quantization; Right panels: semiclassical approach.}
 \label{fig:N8Pad}
\end{figure}

@@

\begin{figure}[htbp]
 \begin{center}
%  \includegraphics[width=60mm,angle=-90]{images/N16ex_energy.eps}
 \end{center}
 \caption{Excitation energies of $\ket{0_2^+}$, $\ket{0_3^+}$ and $\ket{0_4^+}$ in $N=16$ system.}
 \label{fig:N16energy}
\end{figure}

\begin{figure}[htbp]
 \begin{minipage}{1\hsize}
 \begin{center}
  \includegraphics[width=67mm,angle=-90]{images/N16Xeq0p5occ.eps}
 \end{center}
 \end{minipage}
 \begin{minipage}{1\hsize}
 \begin{center}
  \includegraphics[width=67mm,angle=-90]{images/N16Xeq2occ.eps}
 \end{center}
 \end{minipage}
 \caption{Occupation probability in excited $0^+$ states as a function of $\pi$ in $N=50$ system. The upper and lower panels display the results for $x=0.05$ and $x=0.2$, respectively. From the physical meaning of $\pi$, $-4$ corresponds to 0p0h configuration, $-3$ corresponds to 2p2h configuration, and so on.}
 \label{fig:N16_occ}
\end{figure}

\begin{figure}[htbp]
 \begin{minipage}{0.33\hsize}
 \begin{center}
%  \includegraphics[width=70mm,angle=-90]{images/N16Pad_exact.eps}
 \end{center}
 \captionsetup{labelformat=empty,labelsep=none}
 \end{minipage}
 \begin{minipage}{0.33\hsize}
 \begin{center}
%  \includegraphics[width=70mm,angle=-90]{images/N16Pad_Type1.eps}
 \end{center}
 \captionsetup{labelformat=empty,labelsep=none}
 \end{minipage}
 \begin{minipage}{0.33\hsize}
 \begin{center}
%  \includegraphics[width=70mm,angle=-90]{images/N16Pad_semiclassical.eps}
 \end{center}
 \captionsetup{labelformat=empty,labelsep=none}
 \end{minipage}
 \caption{The strength of pair additional transition from $N=14$ to $N=16$ system defined in (\ref{Pad}). The results of $\ket{0_1^+}\to\ket{0_1^+}$, $\ket{0_1^+}\to\ket{0_2^+}$, $\ket{0_2^+}\to\ket{0_1^+}$ and $\ket{0_2^+}\to\ket{0_2^+}$ are shown. Left panels: exact solution; Middle panels: canonical quantization; Right panels: semiclassical approach.}
 \label{fig:N16Pad}
\end{figure}
%In realistic type, semiclassical approach is much better than canonical quantization in every physical values, especially in two-particle transition. The most difficult case is closed shell system with BCS phase transition. However, semiclassical approach works well in closed shell system except phase transition region.

@@

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=50mm,angle=-90]{images/N8p_E.eps}
 \end{center}
 \caption{Pairing gap $\Delta$ in (\ref{Delta_BCS}) as a function of $\pi$ with various pairing strength in $N=8$ system.}
 \label{fig:p_Delta1}
\end{figure}

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=50mm,angle=-90]{images/N16p_E.eps}
 \end{center}
 \caption{Pairing gap $\Delta$ in (\ref{Delta_BCS}) as a function of $\pi$ with various pairing strength in $N=16$ system.}
 \label{fig:p_Delta2}
\end{figure}

\begin{figure}[htbp]
 \begin{center}
%  \includegraphics[width=130mm,angle=-90]{images/Delta_compare.eps}
 \end{center}
 \caption{Energy surface with respect to $\Delta$. The results correspond to Section 4.2, $N=16$ system. Purple lines are obtained from (\ref{mapping}) and green dashed lines are obtained from (\ref{CBCS}). The blue lines are excitation energy spectra until 3rd excitation obtained from (\ref{Sommerfeld}). The top, middle and bottom panels display the energy surfaces with various pairing strength.}
 \label{fig:Delta_E}
\end{figure}

@@

>>>>

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=60mm,angle=-90]{images/phase.eps}
 \end{center}
 \caption{Energy contour plot for $\Omega_1=\Omega_2=8$ and $N=16$.
	The lines indicate the TDHFB trajectories fulfilling
	the EBK quantization condition of Eq. (\ref{EBK}).
	}
 \label{fig:phase_space}
\end{figure}

@@

We apply semiclassical approach to the two-level pairing model.
The invariant measure in SU(2)$\otimes$SU(2) is 
\begin{align}
%	d\mu(Z) &= \prod_{l=1,2} \frac{S_l+1}{\pi}(1+|Z_l|^2)^{-2}d{\rm Re}Z_ld{\rm Im}Z_l \\
%  &= \prod_l \frac{S_l+1}{4\pi}\sin{\theta_l}d\theta_ld\phi_l \\
%  &= \frac{S_1+1}{4\pi}\frac{S_2+1}{4\pi}\frac{1}{S_1S_2}d\Phi d\Pi d\phi d\pi .
d\mu(Z) &= \prod_l \frac{\Omega_l+2}{2\pi}(1+|Z_l|^2)^{-2}d{\rm Re}Z_ld{\rm Im}Z_l \\
  &= \prod_l \frac{\Omega_l+2}{8\pi}\sin{\theta_l}d\theta_ld\phi_l \\
	&= \left(\prod_{l=1,2} \frac{1+2\Omega_l^{-1}}{4\pi}\right)
             d\Phi dJ d\phi dj .
\end{align}
In the last equation, we transform the canonical coordinates
by Eqs. (\ref{phi}) and (\ref{pi}).
%In two-level system, we can transform the canonical coordinates by (\ref{phi}) and (\ref{pi}).
%After coordinate transformation, the Hamilton's equations are
%\begin{align}
%\left\{
%\begin{array}{c}
%  \dot{\Phi} = \frac{\partial\mathcal{H}}{\partial \Pi} \\
%  \dot{\Pi} = -\frac{\partial\mathcal{H}}{\partial \Phi} 
%\end{array}
%\right. \hspace{10mm} \left\{
%\begin{array}{c}
%  \dot{\phi} = \frac{\partial\mathcal{H}}{\partial \pi} \\
%  \dot{\pi} = -\frac{\partial\mathcal{H}}{\partial \phi} 
%\end{array}
%\right. , \label{Hamilton}
%\end{align}
%and the measure and action integral become
%\begin{align}
%  d\mu(Z) &= \frac{S_1+1}{4\pi}\frac{S_2+1}{4\pi}\frac{1}{S_1S_2}d\Phi d\Pi d\phi d\pi \\
%  \mathcal{T}(Z) &=  \int (\Pi d\Phi+\pi d\phi) = \Pi\Phi + \int \pi d\phi.
%\end{align}
%The above canonical variables contain an invariant number $\Pi$. Because two-level system has 2*2 dimensional phase space, we need to find another conservative number before applying (\ref{semi_wave_func}). This task can be accomplished by canonical transformation 
Since the particle number $J=N/2$ and the total energy $E$ are invariant,
the two-level pairing model is integrable.
Thus, we can construct the semiclassical wave function using
Eq. (\ref{semi_wave_func}).
%This task can be accomplished by canonical transformation 
%\begin{align}
%  (\phi, \pi)  \to (t, E)
%\end{align}
%where $E$ is total energy in classical system.
The action integral is given by
\begin{equation}
	\mathcal{T}_k(\Phi,\phi;J)
%	= \Pi\Phi + \int \pi(t) \frac{d\phi}{dt} dt .
	= J\Phi + \int^\phi_{-\pi} j' d\phi' 
	= \frac{N}{2}\Phi + \int^t_0   %_{\mathcal{H}(\phi,\pi)=E_k}
	j(t') \frac{d\phi}{dt'} dt' 
\equiv \mathcal{T}_{N,E_k}(\Phi,t) ,
\end{equation}
where the integration $\int j d\phi$ is performed on the $k$-th
closed trajectory of Eq. (\ref{EBK}), and
the variables $(\phi,j)$ are transformed into $(t,E)$.
%where $\pi(t)$ can be solved from the right side of (\ref{TDHFB_equation}). (i.e. 2D Runge-Kutta method) \par
The semiclassical wave function fulfilling the EBK quantization condition
becomes
\begin{align}
	\ket{\phi_k^N} &\propto \oint d\Phi \oint dt
	e^{i\mathcal{T}_{N,E_k}(\Phi, t)}
	\ket{\Phi,t}_{N,E_k} \label{semi_wave_func0} \\
%  &\propto \sum_k \frac{1}{k!}\int_0^{2\pi}d\Phi e^{i(\Pi-k)\Phi}\sum_{j=0}^{k}C_j^{(E,k)}\ket{S_1,-S_1+j;S_2,-S_2+(k-j)} \label{semi_wave_func1}
  &\propto \sum_{m=0}^{J}C_m^{(E_k,J)}\ket{S_1,-S_1+m;S_2,-S_2+(J-m)} ,
	\label{semi_wave_func1}
\end{align}
with $S_l=\Omega_l/2$, $J=N/2$, and the coefficients
\begin{align}
  C_m^{(E_k,J)} &= {}_J C_m\int_0^T dt \exp{\left( i\int^t j(t') \dot{\phi}(t') dt'-i(J/2-m)\phi(t) \right)}A(q_1,S_1,m)A(q_2,S_2,J-m) ,\\
  & \hspace{5mm} A(q,S,m) = \left(\frac{1-q}{2}\right)^{m/2}\left(\frac{1+q}{2}\right)^{S-m/2}\sqrt{\frac{(2S)!m!}{(2S-m)!}}, \hspace{5mm} \nonumber
\end{align}
where $T$ is the period of the closed trajectory.
The TDHFB-requantized wave functions (\ref{semi_wave_func1}) are
eigenstates of the total particle number.
This is due to the integration over the global gauge angle $\Phi$,
which makes the particle number projection not only for the ground state
but also for excited states.
See Appendix for detailed derivation of Eq.~(\ref{semi_wave_func1}).

@@

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=60mm,angle=-90]{images/N50ex_energy2.eps}
 \end{center}
 \caption{Excitation energies of $\ket{0_2^+}$, $\ket{0_3^+}$ and $\ket{0_4^+}$ in $N=50$ system.}
 \label{fig:N50energy}
\end{figure}

\begin{figure}[htbp]
 \begin{minipage}{1\hsize}
 \begin{center}
  \includegraphics[width=67mm,angle=-90]{images/N50Xeq0p5occ.eps}
 \end{center}
 \end{minipage}
 \begin{minipage}{1\hsize}
 \begin{center}
  \includegraphics[width=67mm,angle=-90]{images/N50Xeq2occ.eps}
 \end{center}
 \end{minipage}
 \caption{Occupation probability in excited $0^+$ states as a function of $j$ in $N=50$ system. The upper and lower panels display the results for $x=0.5$ and $x=2$, respectively. From (\ref{momentum}), $j=-12.5$ corresponds to 0p50h configuration, $j=-11.5$ corresponds to 2p52h configuration, and so on.}
 \label{fig:N50_occ}
\end{figure}

\begin{figure}[htbp]
 \begin{minipage}{0.3\hsize}
 \begin{center}
  \includegraphics[width=70mm,angle=-90]{images/N50Pad_CQ.eps}
 \end{center}
 \captionsetup{labelformat=empty,labelsep=none}
 \end{minipage}
 \begin{minipage}{0.3\hsize}
 \begin{center}
  \includegraphics[width=70mm,angle=-90]{images/N50Pad_FD.eps}
 \end{center}
 \captionsetup{labelformat=empty,labelsep=none}
 \end{minipage}
 \begin{minipage}{0.3\hsize}
 \begin{center}
  \includegraphics[width=70mm,angle=-90]{images/N50Pad_SPA.eps}
 \end{center}
 \captionsetup{labelformat=empty,labelsep=none}
 \end{minipage}
 \caption{The strength of pair additional transition $B(P_{\rm ad};k\rightarrow k')$ from $N=48$ to $N=50$ system. Dashed lines are exact solution. Upper parts are the transition of $\ket{0_1^+}\to\ket{0_1^+}$ and $\ket{0_2^+}\to\ket{0_2^+}$, lower parts are the transition of $\ket{0_1^+}\to\ket{0_2^+}$, $\ket{0_2^+}\to\ket{0_1^+}$. Left panels: CQ1; Middle panels: FD; Right panels: SPA.}
 \label{fig:N50Pad}
\end{figure}

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=60mm,angle=-90]{images/N100ex_energy2.eps}
 \end{center}
 \caption{Excitation energies of $\ket{0_2^+}$, $\ket{0_3^+}$ and $\ket{0_4^+}$ in $N=100$ system.}
 \label{fig:N100energy}
\end{figure}

\begin{figure}[htbp]
 \begin{minipage}{1\hsize}
 \begin{center}
  \includegraphics[width=67mm,angle=-90]{images/N100Xeq0p5occ.eps}
 \end{center}
 \end{minipage}
 \begin{minipage}{1\hsize}
 \begin{center}
  \includegraphics[width=67mm,angle=-90]{images/N100Xeq2occ.eps}
 \end{center}
 \end{minipage}
 \caption{Occupation probability in excited $0^+$ states as a function of $j$ in $N=100$ system. The upper and lower panels display the results for $x=0.5$ and $x=2$, respectively. From (\ref{momentum}), $j=-25$ corresponds to 0p0h configuration, $j=-24$ corresponds to 2p2h configuration, and so on.}
 \label{fig:N100_occ}
\end{figure}

\begin{figure}[htbp]
 \begin{minipage}{0.3\hsize}
 \begin{center}
  \includegraphics[width=70mm,angle=-90]{images/N100Pad_CQ.eps}
 \end{center}
 \captionsetup{labelformat=empty,labelsep=none}
 \end{minipage}
 \begin{minipage}{0.3\hsize}
 \begin{center}
  \includegraphics[width=70mm,angle=-90]{images/N100Pad_FD.eps}
 \end{center}
 \captionsetup{labelformat=empty,labelsep=none}
 \end{minipage}
 \begin{minipage}{0.3\hsize}
 \begin{center}
  \includegraphics[width=70mm,angle=-90]{images/N100Pad_SPA.eps}
 \end{center}
 \captionsetup{labelformat=empty,labelsep=none}
 \end{minipage}
 \caption{The strength of pair additional transition $B(P_{\rm ad};k\rightarrow k')$ from $N=98$ to $N=100$ system. Dashed lines are exact solution. Upper parts are the transition of $\ket{0_1^+}\to\ket{0_1^+}$ and $\ket{0_2^+}\to\ket{0_2^+}$, lower parts are the transition of $\ket{0_1^+}\to\ket{0_2^+}$, $\ket{0_2^+}\to\ket{0_1^+}$. Left panels: CQ1; Middle panels: FD; Right panels: SPA.}
 \label{fig:N100Pad}
\end{figure}

@@

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=60mm,angle=-90]{images/N8ex_energy2.eps}
 \end{center}
 \caption{Excitation energies of $\ket{0_2^+}$, $\ket{0_3^+}$ and $\ket{0_4^+}$ in $N=8$ system.}
 \label{fig:N8energy}
\end{figure}

\begin{figure}[htbp]
 \begin{minipage}{1\hsize}
 \begin{center}
  \includegraphics[width=67mm,angle=-90]{images/N8Xeq0p5occ.eps}
 \end{center}
 \end{minipage}
 \begin{minipage}{1\hsize}
 \begin{center}
  \includegraphics[width=67mm,angle=-90]{images/N8Xeq2occ.eps}
 \end{center}
 \end{minipage}
 \caption{Occupation probability in excited $0^+$ states as a function of $j$ in $N=8$ system. The upper and lower panels display the results for $x=0.05$ and $x=0.2$, respectively. From (\ref{momentum}), $j=-2$ corresponds to 0p8h configuration, $j=-1$ corresponds to 2p10h configuration, and so on.}
 \label{fig:N8_occ}
\end{figure}

\begin{figure}[htbp]
 \begin{minipage}{0.3\hsize}
 \begin{center}
  \includegraphics[width=70mm,angle=-90]{images/N8Pad_CQ.eps}
 \end{center}
 \captionsetup{labelformat=empty,labelsep=none}
 \end{minipage}
 \begin{minipage}{0.3\hsize}
 \begin{center}
  \includegraphics[width=70mm,angle=-90]{images/N8Pad_FD.eps}
 \end{center}
 \captionsetup{labelformat=empty,labelsep=none}
 \end{minipage}
 \begin{minipage}{0.3\hsize}
 \begin{center}
  \includegraphics[width=70mm,angle=-90]{images/N8Pad_SPA.eps}
 \end{center}
 \captionsetup{labelformat=empty,labelsep=none}
 \end{minipage}
 \caption{The strength of pair additional transition $B(P_{\rm ad};k\rightarrow k')$ from $N=6$ to $N=8$ system. Dashed lines are exact solution. Upper parts are the transition of $\ket{0_1^+}\to\ket{0_1^+}$ and $\ket{0_2^+}\to\ket{0_2^+}$, lower parts are the transition of $\ket{0_1^+}\to\ket{0_2^+}$, $\ket{0_2^+}\to\ket{0_1^+}$. Left panels: CQ1; Middle panels: FD; Right panels: SPA.}
 \label{fig:N8Pad}
\end{figure}

@@

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=60mm,angle=-90]{images/N16ex_energy2.eps}
 \end{center}
 \caption{Excitation energies of $\ket{0_2^+}$, $\ket{0_3^+}$ and $\ket{0_4^+}$ in $N=16$ system.}
 \label{fig:N16energy}
\end{figure}

\begin{figure}[htbp]
 \begin{minipage}{1\hsize}
 \begin{center}
  \includegraphics[width=67mm,angle=-90]{images/N16Xeq0p5occ.eps}
 \end{center}
 \end{minipage}
 \begin{minipage}{1\hsize}
 \begin{center}
  \includegraphics[width=67mm,angle=-90]{images/N16Xeq2occ.eps}
 \end{center}
 \end{minipage}
 \caption{Occupation probability in excited $0^+$ states as a function of $j$ in $N=16$ system. The upper and lower panels display the results for $x=0.05$ and $x=0.2$, respectively.From (\ref{momentum}), $-4$ corresponds to 0p0h configuration, $-3$ corresponds to 2p2h configuration, and so on.}
 \label{fig:N16_occ}
\end{figure}

\begin{figure}[htbp]
 \begin{minipage}{0.3\hsize}
 \begin{center}
  \includegraphics[width=70mm,angle=-90]{images/N16Pad_CQ.eps}
 \end{center}
 \captionsetup{labelformat=empty,labelsep=none}
 \end{minipage}
 \begin{minipage}{0.3\hsize}
 \begin{center}
  \includegraphics[width=70mm,angle=-90]{images/N16Pad_FD.eps}
 \end{center}
 \captionsetup{labelformat=empty,labelsep=none}
 \end{minipage}
 \begin{minipage}{0.3\hsize}
 \begin{center}
  \includegraphics[width=70mm,angle=-90]{images/N16Pad_SPA.eps}
 \end{center}
 \captionsetup{labelformat=empty,labelsep=none}
 \end{minipage}
 \caption{The strength of pair additional transition $B(P_{\rm ad};k\rightarrow k')$ from $N=14$ to $N=16$ system. Dashed lines are exact solution. Upper parts are the transition of $\ket{0_1^+}\to\ket{0_1^+}$ and $\ket{0_2^+}\to\ket{0_2^+}$, lower parts are the transition of $\ket{0_1^+}\to\ket{0_2^+}$, $\ket{0_2^+}\to\ket{0_1^+}$. Left panels: CQ1; Middle panels: FD; Right panels: SPA.}
 \label{fig:N16Pad}
\end{figure}
%In realistic type, semiclassical approach is much better than canonical quantization in every physical values, especially in two-particle transition. The most difficult case is closed shell system with BCS phase transition. However, semiclassical approach works well in closed shell system except phase transition region.

@@

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=50mm,angle=-90]{images/N8p_E.eps}
 \end{center}
 \caption{Energy surface with respect to $j$ in $x=0.5$, $x=2$ and $x=3.2$, in $\Omega=8$ and $N=8$ system.
 Dashed line is pairing deformation parameter $\alpha$ in (\ref{Delta_BCS}) as a function of $j$.}
 \label{fig:p_Delta1}
\end{figure}

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=50mm,angle=-90]{images/N16p_E.eps}
 \end{center}
 \caption{Energy surface with respect to $j$ in $x=0.5$, $x=2$ and $x=3.2$, in $\Omega=8$ and $N=16$ system.
 Dashed line is pairing deformation parameter $\alpha$ in (\ref{Delta_BCS}) as a function of $j$.}
 \label{fig:p_Delta2}
\end{figure}

\begin{figure}[htbp]
 \begin{minipage}{0.45\hsize}
 \begin{center}
  \includegraphics[width=130mm,angle=-90]{images/N50gap_E.eps}
 \end{center}
 \end{minipage}
 \begin{minipage}{0.45\hsize}
 \begin{center}
  \includegraphics[width=130mm,angle=-90]{images/N16gap_E.eps}
 \end{center}
\end{minipage}
 \caption{Energy surface with respect to $\alpha$ in $x=0.5$, $x=1$ and $x=2$. 
Green lines are energy spectra until 3rd excitation obtained from CQ2 
(Sec.~\ref{subsec:canonical2}). Left panels: $\Omega=50$, $N=50$ system;
 Right panels: $\Omega=8$, $N=16$ system.}
 \label{fig:Delta_E}
\end{figure}

@@

\appendix
\section{Derivation of semiclassical wave function}
